Multi-level modeling with Openflexo/\FML

### 2021-09-27 responseLetter.tex

\Reviewer{\#1}
\begin{response}{In section 2 Technology the authors describe the foundations of the Openflexo approach. Here it would greatly help the reader to see an example how the approach works for traditional modeling languages. For example, how would you realize a small subset of BPMN with the approach? This could briefly be illustrated so as to give the reader an immediate understanding. Especially, the 'metamodel'-agnostic approach seems very interesting but I would like to see how that is used for traditional modeling approaches.}
TODO.

Voici la figure avec la connexion externe

\begin{figure}[t]
    \centering
    \includegraphics[width=1.0 \textwidth]{Figures/BPMNSubsetExampleWithExternalConnexion.pdf}
    \caption{An example of BPMN subset built on top of a BPMN/EMF model}
    \label{fig:BPMNSubsetExample}
\end{figure}

\begin{lstlisting}
use org.openflexo.technologyadapter.emf.EMFModelSlot as EMF;
import ["http://www.omg.org/spec/BPMN/20100524/MODEL-XMI"] as BPMN_METAMODEL;

// A simplified BPMN metamodel exposing
// both concepts BPMNProcess and BPMNTask
model SimplifiedBPMN {

  // Connexion to a .bpmn file
  EMFModel bpmnModel 
    with EMF::EMFModelSlot(
        metaModel = BPMN_METAMODEL);

  // Abstract concept BPMNElement defining
  // a name and a link to an eventual BPMNElement
  // in .bpmn file
  abstract concept BPMNElement {
  	EMFObjectIndividual bpmnElement 
  	    with EMF::EMFObjectIndividualRole (
			source = bpmnModel
		);
    String name values bpmnElement.name;
  }

  concept BPMNProcess extends BPMNElement {

    // Describe here properties and
    // behaviours for BPMNProcess concept
    ...

    concept BPMNTask extends BPMNElement {

        // Describe here properties and
        // behaviours for BPMNTask concept
        ...

    }

    // Other core concepts
  }
}
\end{lstlisting}

### 2021-09-27 4-technology.tex
Somme more changes in the related work.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{Figures/FMLCoreModel.pdf}
    \caption{The \FML core metamodel}
    \label{fig:mm}
\end{figure}
%\noteAntoine{Dans la figure ne manque-t-il pas les containements ? (VM vers Concepts)}

@@

@@

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=1.0 \textwidth]{Figures/FMLMetaModel.pdf}
    \caption{Representation of the main concepts of \FML language}
    \label{fig:mm}
\end{figure*}
%\noteAntoine{Dans la figure ne manque-t-il pas les containements ? (VM vers Concepts)}
%\noteSylvain{C'est le cas dans cette nouvelle figure}

@@

@@

\noteSylvain{Retravailler le texte pour parler de tous les concepts qui sont sur la figure}

@@

%\noteSylvain{Tentative de représenter ici un sous-ensemble de BPMN en montrant la capacité du language FML à faire de la modélisation conceptuelle d'une part, mais aussi à fédérer des nouveaux concepts avec un modèle et un métamodèle existant.}

%\noteSylvain{On explique dans la suite que dans le challenge, on ne va pas exploiter l'aspect fédération de modèle (sauf pour la partie diagramme - c'est expliqué plus haut également - ).}

Figure \ref{fig:BPMNSubsetExample} shows...

%\noteSM{We use the current Figure 3 to answer reviewer 1 in the response letter just as to show how the model federation works, but not here.}

\noteSylvain{Rédiger l'explication...}

\begin{figure}[t]
    \centering
    \includegraphics[width=\columnwidth]{Figures/BPMNSubsetExample.pdf}
    \caption{An example of BPMN subset showing both the model and an instance of that model}
    \label{fig:BPMNSubsetExample}
\end{figure}

\begin{lstlisting}
// A simplified BPMN metamodel exposing
// both concepts BPMNProcess and BPMNTask
model SimplifiedBPMN {

  // Abstract concept BPMNElement defining
  // a name
  abstract concept BPMNElement {
    String name;
  }

  concept BPMNProcess extends BPMNElement {

    // Describe here properties and
    // behaviours for BPMNProcess concept
    ...

    concept BPMNTask extends BPMNElement {

        // Describe here properties and
        // behaviours for BPMNTask concept
        ...

    }

    // Other core concepts
  }
}
\end{lstlisting}

\noteSylvain{Faut-il montrer des exemples de comportement aussi ?}
